Meta-analysis

### 2019-10-23 05_MetaAnalysis.Rmd
Added chunks for start of season rainfall and end of season rainfall.
Edited rainfall lm plots

```{r MEsummary_Libraries, message=FALSE}
install.packages("tidyverse")
install.packages("devtools")
devtools::install_github("https://github.com/PaulMelloy/bomrang")
devtools::install_github("https://github.com/adamhsparks/theme.usq")

@@

```{r yield_from_rain}
experiment_sites <- read.csv("data/Mungbean_experiment_sites.csv", stringsAsFactors = FALSE)

@@

rain_dat_sum <- rain_dat %>%
   group_by(trial_ref) %>%
   summarise(location = unique(location),
             planting_date = unique(as.character(planting_date))[1],
             grain_yield = mean(grain_yield.t.ha., na.rm = TRUE))

@@

rain_dat_sum$lat <- NA
rain_dat_sum$lon <- NA

# 
rain_dat_sum[rain_dat_sum$location == "Bongeen_1", c("lat","lon")] <- 
   experiment_sites[experiment_sites$location == "Bongeen 1 & 2",c("lat","lon")]

@@

rain_dat_sum[rain_dat_sum$location == "Dalby", c("lat","lon")] <- c(-27.168426, 151.264421)

rain_dat_sum$rainfall_sum <- NA

source("R/AUS_rainfall_function.r")
# loop to download and save all the rainfall sum data

for(j in -10:20){
   if(j == -10){lm_data <- data.frame()}

@@

         rain_dat_sum$rainfall_sum[i] <- 
            AUS_rainfall(StartDate = as.Date(rain_dat_sum$planting_date)[i] + 10,
                         EndDate = as.Date(rain_dat_sum$planting_date)[i] + 90,
                         lat = rain_dat_sum$lat[i],
                         long = rain_dat_sum$lon[i])

      }
   }

@@

   lm_data <- rbind(lm_data,
                    data.frame(days_from_plant = 10,
                               estimate = coef(lmod1)[2,1],
                               P_value = coef(lmod1)[2,4],
                               r_squared = lmod1$r.squared,
                               adj_r_squared = lmod1$adj.r.squared,
                               stringsAsFactors = FALSE)
                    )

#write.csv(lm_data, "data/rainfall_x_Gyield_lmod.csv")
lm_data <- read.csv("data/rainfall_x_Gyield_lmod.csv", stringsAsFactors = FALSE)
rain_dat_sum[rain_dat_sum$location != "Hermitage",] %>%
   ggplot(aes(x = rainfall_sum, y = grain_yield )) + 
   geom_point(aes(colour = location)) +
   geom_smooth(method = "lm")

@@

is.vector(unlist(c(rain_dat_sum[1,5],rain_dat_sum[1,6])))

plot(P_value ~ days_from_plant, data = lm_data)
plot(r_squared ~ days_from_plant, data = lm_data)
plot(estimate ~ days_from_plant, data = lm_data)

tmp1 <- read.csv("C:/Users/U8011054/AppData/Local/Temp/RtmpkbEvfL/IDCJAC0009_041359_1800_Data.csv", stringsAsFactors = FALSE)

nchar(tmp1$Bureau.of.Meteorology.station.number[1])
strsp

head(tmp1)
message()

@@

FS_dates <- data.frame(first_sign = as.Date(unique(PM_MB_means$first_sign_disease)),
                       plant.date = as.Date(PM_MB_)
)

PM_MB_

dat1 <- data.frame(First_sign = sort(format(FS_dates, "%b-%d"))[c(5:25,1:4)])

dat1$First_sign <- as.Date(dat1$First_sign)

ggplot(dat1, aes(x = First_sign))+
   geom_dotplot()+
   scale_x_date()+
   coord_flip()

@@

>>>>

```{r MEsummary_Libraries, message=FALSE}
# install.packages("tidyverse")
# install.packages("devtools")
# devtools::install_github("https://github.com/PaulMelloy/bomrang")
# devtools::install_github("https://github.com/adamhsparks/theme.usq")
# install.packages("lme4")

@@

In crop rain could be a significant factor which contributes to the end of season grain yield. To investigate any relationship I will loop a linear model over time periods from 10 days prior to planting, to 100 days after planting.

```{r yield_from_rain_DataRangle}
# Import the information for each experimental site
experiment_sites <- read.csv("data/Mungbean_experiment_sites.csv", stringsAsFactors = FALSE)

@@

# Create data set for which we will input the sum in-crop rainfall
rain_dat_sum <- rain_dat %>%
   group_by(trial_ref) %>%
   summarise(location = unique(location),
             planting_date = unique(as.character(planting_date))[1],
             grain_yield = mean(grain_yield.t.ha., na.rm = TRUE))

@@

# add columns for lat and lon
rain_dat_sum$lat <- NA
rain_dat_sum$lon <- NA

# Input lat and lon to dataframe for each experimental location
rain_dat_sum[rain_dat_sum$location == "Bongeen_1", c("lat","lon")] <- 
   experiment_sites[experiment_sites$location == "Bongeen 1 & 2",c("lat","lon")]

@@

rain_dat_sum[rain_dat_sum$location == "Dalby", c("lat","lon")] <- c(-27.168426, 151.264421)
```

Loop over the dates at the start of the season (to 90 days after planting) to find which date fits the best linear model for grain weight and in-crop rainfall.
```{r rainfall_sum_Sstart}
# add column for sum in-crop rainfall
rain_dat_sum$rainfall_sum <- NA

# source funtion that uses bomrang get_historical to return the sum rainfall between two dates
source("R/AUS_rainfall_function.r")
# loop to download and save all the rainfall sum data
# this first loop Investigate when is the first day in the season for which in-crop rainfall is important

for(j in -20:20){
   if(j == -20){lm_data <- data.frame()}

@@

         rain_dat_sum$rainfall_sum[i] <- 
            AUS_rainfall(StartDate = (as.Date(rain_dat_sum$planting_date)[i] + j),
                         EndDate = (as.Date(rain_dat_sum$planting_date)[i] + 90 ),
                         lat = rain_dat_sum$lat[i],
                         long = rain_dat_sum$lon[i])

@@

      lm_data <- rbind(lm_data,
                    data.frame(days_from_plant = j,
                               estimate = coef(lmod1)[2,1],
                               P_value = coef(lmod1)[2,4],
                               r_squared = lmod1$r.squared,
                               adj_r_squared = lmod1$adj.r.squared,
                               stringsAsFactors = FALSE)
                    )

   } # If it aborts with an error Error in row_start:(row_start + season) : argument of length 0, just re-run the code

plot(log(P_value) ~ days_from_plant, data = lm_data)
abline(v = lm_data[lm_data$P_value == min(lm_data$P_value),"days_from_plant"])
plot(r_squared ~ days_from_plant, data = lm_data)
abline(v = lm_data[lm_data$r_squared == max(lm_data$r_squared),"days_from_plant"])
plot(estimate ~ days_from_plant, data = lm_data)
abline(v = 14, h = lm_data[lm_data$r_squared == max(lm_data$r_squared),"estimate"], col = "grey")
```

```{r rainfall_sum_SEnd}

# Loop to find the last day in the season for which in crop rainfall is important
for(j in -20:20){
   if(j == -10){lm_data <- data.frame()}

         rain_dat_sum$rainfall_sum[i] <- 
            AUS_rainfall(StartDate = (as.Date(rain_dat_sum$planting_date)[i] + 11),
                         EndDate = (as.Date(rain_dat_sum$planting_date)[i] + 90 + j),
                         lat = rain_dat_sum$lat[i],
                         long = rain_dat_sum$lon[i])

      lm_data <- rbind(lm_data,
                    data.frame(days_from_plant = j,
                               estimate = coef(lmod1)[2,1],
                               P_value = coef(lmod1)[2,4],
                               r_squared = lmod1$r.squared,
                               adj_r_squared = lmod1$adj.r.squared,
                               stringsAsFactors = FALSE)
                    )

plot(P_value ~ days_from_plant, data = lm_data)
abline(v = -3)
abline(h = 0.00315, col = "grey")
plot(r_squared ~ days_from_plant, data = lm_data)
abline(v = -3)
abline(h = 0.562, col = "grey")
plot(estimate ~ days_from_plant, data = lm_data)
abline(v = -3)

#write.csv(lm_data, "data/rainfall_x_Gyield_lmod.csv")

lm_data <- read.csv("data/rainfall_x_Gyield_lmod.csv", stringsAsFactors = FALSE)
rain_dat_sum[rain_dat_sum$location != "Hermitage",] %>%
   ggplot(aes(x = rainfall_sum, y = grain_yield )) + 
   geom_point(aes(colour = location)) +
   geom_smooth(method = "lm")

@@

```
The approximate period when in-crop rainfall impacts the most on the mean harvest is bettween 11 - 88 days after planting.

@@

season_dates <- PM_MB_means %>%
   group_by(trial_ref)%>%
   summarise(Planting_date = unique(planting_date),
             Harvest_date = unique(harvest_date),
             First_sign_PM = unique(first_sign_disease),
             season_length = as.integer(as.Date(unique(harvest_date)) - as.Date(unique(planting_date)))
             )

# function to extract date from the year
# format should be Universal time format
source("R/year2day.r")
year.day(season_dates$Planting_date[5])

season_dates$Planting_day <- unlist(lapply(season_dates$Planting_date,year2day))
season_dates$Disease_day <- unlist(lapply(season_dates$First_sign_PM,year2day))
season_dates$Harvest_day <- season_dates$Planting_day + season_dates$season_length

season_dates[1,"Planting_day"] <- year2day(as.Date("2012-02-28")-7) # planted in december and emerged in February, Assuming due to lack of rain or recording error. Using 7 days prior to emergence day as planting day

first_day_month <- c(0, 31, 59, 90, 120, 151, 181, 211, 243, 273)
axis_labels_date <- c(format(Sys.Date() - year2day(Sys.Date()) + first_day_month[1], "%b-%d"),  # Jan
                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[2], "%b-%d"), # Feb
                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[3], "%b-%d"), # March
                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[4], "%b-%d"), # April
                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[5], "%b-%d"), # May
                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[6], "%b-%d"), # June
                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[7], "%b-%d"), # July
                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[8], "%b-%d"), # August
                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[9], "%b-%d"), # Sept
                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[10], "%b-%d") # October
                         )

# reorder the factors so they will appear in chronilogical order
# I used First sign because all trials have recorded this
season_dates$trial_ref <- factor(season_dates$trial_ref, levels = levels(season_dates$trial_ref)[rev(order(season_dates$First_sign_PM))])

season_dates %>%
   ggplot()+
   geom_pointrange(aes(x = trial_ref, y = Disease_day, ymin = Planting_day, ymax = Harvest_day))+
   scale_y_continuous(
      limits = c(0, max(season_dates$Planting_day + 
                           season_dates$season_length, 
                        na.rm = TRUE)),
      labels = axis_labels_date,
      breaks = first_day_month
   )+
   geom_point(aes(x = trial_ref, y = Disease_day))+
   coord_flip()+
   ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")

    scale_x_continuous(
      limits = c(0, 200),
      labels = c(),
      breaks = c(1, 50, 100, 150, 200)
   )

@@

head(season_dates)
